% \documentclass[paper=a4, fontsize=11pt]{scrartcl} % A4 paper and 11pt font size
%
% \usepackage{hyperref}% in order to use hyperlinks
% \usepackage[T1]{fontenc} % Use 8-bit encoding that has 256 glyphs
% %\usepackage{fourier} % Use the Adobe Utopia font for the document - comment this line to return to the LaTeX default
% \usepackage[english]{babel} % English language/hyphenation
% \usepackage{amsmath,amsfonts,amsthm} % Math packages
% \usepackage{graphicx}
% \usepackage{epstopdf}
% \DeclareGraphicsExtensions{.eps}
% \usepackage{subcaption}
%
% %\usepackage{lipsum} % Used for inserting dummy 'Lorem ipsum' text into the template
%
% %\usepackage{sectsty} % Allows customizing section commands
% %\allsectionsfont{\centering \normalfont\scshape} % Make all sections centered, the default font and small caps
%
% \usepackage{fancyhdr} % Custom headers and footers
% \pagestyle{fancyplain} % Makes all pages in the document conform to the custom headers and footers
% \fancyhead{} % No page header - if you want one, create it in the same way as the footers below
% \fancyfoot[L]{} % Empty left footer
% \fancyfoot[C]{} % Empty center footer
% \fancyfoot[R]{\thepage} % Page numbering for right footer
% \renewcommand{\headrulewidth}{0pt} % Remove header underlines
% \renewcommand{\footrulewidth}{0pt} % Remove footer underlines
% \setlength{\headheight}{13.6pt} % Customize the height of the header
%
% \numberwithin{equation}{section} % Number equations within sections (i.e. 1.1, 1.2, 2.1, 2.2 instead of 1, 2, 3, 4)
% \numberwithin{figure}{section} % Number figures within sections (i.e. 1.1, 1.2, 2.1, 2.2 instead of 1, 2, 3, 4)
% \numberwithin{table}{section} % Number tables within sections (i.e. 1.1, 1.2, 2.1, 2.2 instead of 1, 2, 3, 4)
%
% \setlength\parindent{0pt} % Removes all indentation from paragraphs - comment this line for an assignment with lots of text
%
% %----------------------------------------------------------------------------------------
% %	TITLE SECTION
% %----------------------------------------------------------------------------------------
%
% \newcommand{\horrule}[1]{\rule{\linewidth}{#1}} % Create horizontal rule command with 1 argument of height
%
% \title{
% \normalfont \normalsize
% \textsc{CINVESTAV, Automatic Control Department} \\ [25pt] % Your university, school and/or department name(s)
% \horrule{0.5pt} \\[0.4cm] % Thin top horizontal rule
% \huge Benford's Law in Dynamical Systems \\ % The assignment title
% \horrule{2pt} \\[0.5cm] % Thick bottom horizontal rule
% }
%
% \author{Emanuel Rocha Campos, Gerardo E. Cardona S\'anchez} % Your name
%
% \date{\normalsize\today} % Today's date or a custom date
%
% \begin{document}

\maketitle % Print the title

%----------------------------------------------------------------------------------------
%	PROBLEM 1
%----------------------------------------------------------------------------------------

\section{Overview}
\input{articulos/2-benford/secciones/Introduction.tex}
%------------------------------------------------

\subsection{Benford's Law}
\input{articulos/2-benford/secciones/Benford.tex}

\subsubsection{Fibonacci Sequence}
\input{articulos/2-benford/secciones/Benford_Fibonacci.tex}

\subsubsection{Mexico's Municipalities Population}
\input{articulos/2-benford/secciones/Benford_Mex_inegi.tex}

\subsection{Autonomous Circuits}
\input{articulos/2-benford/secciones/Autonomous_Circuits.tex}

\subsection{Defining Chaos}
\input{articulos/2-benford/secciones/Chaos.tex}

\subsubsection{Lyapunov Exponent}
\input{articulos/2-benford/secciones/Lyapunov_exponent.tex}

\subsubsection{Chua's Circuit}
\input{articulos/2-benford/secciones/Chua.tex}

\subsubsection{Takougang Circuit}
\input{articulos/2-benford/secciones/Takougang.tex}

\section{Simulations}
\input{articulos/2-benford/secciones/Sim.tex}

%------------------------------------------------
\section{Experimental Results}
\input{articulos/2-benford/secciones/results.tex}

\section{Conclusion}
\input{articulos/2-benford/secciones/Conclusions.tex}
%----------------------------------------------------------------------------------------
%  BIBLIOGRAPHY
\begin{thebibliography}{1}

\bibitem{Benford38}
  Benford Frank,
  \emph{The law of anomalous numbers}.
  Proc. Amer. Philos. Soc. 78,
  (1938),
  551-572.

\bibitem{Nigrini97}
  Nigrini Mark J., Mittermaier Linda J.
  \emph{The use of Benford's Law as an Aid in Analytical Procedures}
  Auditing: A Journal of Practice \& Theory,
  (1997),
  52-67

\bibitem{Kreuzer14}
  Matthias Kreuzer, Denis Jordan, PhD, Bernd Antkowiak, Berthold Drexler, Eberhard F. Kochs, and Gerhard Schneider
  \emph{Brain Electrical Activity Obeys Benford's Law}
  Neuroscience in Anesthesiology and Perioperative Medicine,
  (2014),
  183-191
\bibitem{Strogatz14}
 Steven H. Strogatz
  \emph{Nonlinear Dynamics and Chaos, With Applications to Physics, Biology, Chemistry and Engineering, Second Edition}
  Westview Press,
  (2014),
  309-191
\bibitem{Parlitz92}
  U. Parlitz
  \emph{Lyapunov's Exponent from Chua's Circuit}
  Journal of Circuits, Systems, and Computers,Vol. 3, No.2
  (1992),
  507-523
\bibitem{Kennedy95}
  Michale Peter Kennedy
  \emph{Experimental Chaos from Autonomous Electronic Circuits}
  Phil. Trans. R. Soc. Lond. A,
  (1995),
  507-523

\bibitem{Ayrom86}
Ayrom F.,
 \emph{Chaos in Chua's Circuit},
 IEE Proceedings, Vol. 133, No. 6 307-312
 , 1986,
 307-312


\bibitem{Takougang13}
Sifeu Takougang Kingni, Lars Keuninckx, Paul Woafo,  Guy Van der Sande, Jan Danckaert
\emph{Dissipative chaos, Shilnikov chaos and bursting oscillations
in a three-dimensional autonomous system: theory
and electronic implementation}
Nonlinear Dynamics,
2013

\bibitem{Torres07} Torres J. et al.,
 \emph{How do numbers begin? (The first digit law)},
  Eur. J. Phys., Vol. 28,
   2007,
   17-25

\bibitem{Tolle00}
Charles R. Tolle, Joanne L. Budzien, and Randall A. LaViolette
\emph{Do dynamical systems follow Benford’s law?}
Chaos: An Interdisciplinary Journal of Nonlinear Science 10,
 331,
2000
\bibitem{Perc03}
Perc, M., Marhl, M.
\emph{ Different types of bursting calcium
oscillations in non-excitable cells},
Chaos Solitons Fractals 18,
 759–773
2003
\bibitem{Sherman88}
Sherman, A., Rinzel, J., Keizer, J.
\emph{ Emergence of organized bursting in clusters of pancreatic $\beta$-cells by channel sharing},
Biophys. J. 54, 411–425,
1988
\bibitem{Ermentrout09}
\emph{Mathematical Foundations of Neuroscience}
Interdiscplinary Applied Mathematics 35,
103-126,
2009
\end{thebibliography}

% \end{document}
